---
title       : Time Series Analysis
subtitle    : A Shiny App for Analyzing Time Series Data
author      : 
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Would you like to easily load and plot your time series data?

Now you can use this FREE Shiny App to get a plot like this:

```{r, echo=FALSE, results='hide'}
library(datasets)
library(forecast)
DAXts <- EuStockMarkets[,2]
```

```{r}
plot.ts(DAXts)
```


---

## Would you like to analyze your time series data by adding a regression line?

You can use this FREE Shiny App to add a regression line like this:

```{r, echo=TRUE, fig.height=5, fig.align='center'}
plot.ts(DAXts); abline(lm(DAXts ~ index(DAXts)), col="blue", lwd=3)
```

---

## Would you like to decomposing the observed values into the additive components?

You can use this FREE Shiny App to decomposing the time series like this:

```{r, fig.height=4.5, fig.align='center'}
decomp.DAXts <- decompose(DAXts);  plot(decomp.DAXts)
```

---

## Are you convinced???

Try out this free Shiny App... just go to shinyapps.io !!!


### http://parker-d.shinyapps.io/dpExample



